MLH1 Results Outline

### 2020-05-01 doc/Results_v2.rmd
making triangle plots, and icon drafts

---
title: "MLH1 Results Outline"
bibliography: refs_Main_Report.bib
date: 'null'
output:
  word_document:
    toc: yes
    toc_depth: '5'
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '5'
    toc_float: yes
always_allow_html: yes
---

@@

two.Q1.SC.plots <- {Q1.SC.short.mouse_scatter_boxplot + {Tot.SC_mouse.av_ALL} + plot_layout(ncol = 2, widths = c(1,1), heights = c(1,1)) }

>>>>

---
title: "MLH1 Results Outline"
bibliography: refs_Main_Report.bib
date: 'null'
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '5'
    toc_float: yes
  word_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
---

@@

two.Q1.SC.plots <- {Q1.SC.short.mouse_scatter_boxplot + {Tot.SC_mouse.av_ALL} + plot_layout(ncol = 2, widths = c(1,1), heights = c(1.5,1.5)) }
